---
title: "John Mannion Homework 3"
description: |
  Homework 3 - Discussion of the USArrests data set and a small renaming of the columns for clarity. 
author:
  - name: John Mannion
date: 08-10-2021
output:
  distill::distill_article:
    self_contained: false
draft: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```
```{r}
Crime <- USArrests %>%
 rename(
    Urban.Percent = UrbanPop,
    Murder.Rate = Murder,
    Assault.Rate = Assault,
    Rape.Rate = Rape
    )
```

This data set details the number of arrests per 100,000 residents in a state for murder, assault, and rape in the year 1973. It also lists the percentage of the population that lives in urban areas ("UrbanPop"). There is no missing data for any of these values. 

I renamed the variables in the data set to make more clear what each number represented. "UrbanPop" became "Urban.Percent", "Murder" became "Murder.Rate", 'Rape" became "Rape.Rate", and "Assault" became "Assault.Rate".

